---
title: "README"
author: "Zachary McCaw"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: TRUE
--- 

```{r global_options, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```

# Description

This package provides functions for inference the difference in quantiles and probability indices comparing two treatment arms. 

# Installation

```{R, eval=FALSE}
devtools::install_github(repo = 'zrmacc/Ordinal')
```

# Examples

Simulated example data. 

```{R}
library(Ordinal)
arm0 <- as.numeric(rmultinom(n = 1, size = 200, prob = c(0.25, 0.25, 0.25, 0.25)))
arm1 <- as.numeric(rmultinom(n = 1, size = 200, prob = c(0.10, 0.30, 0.30, 0.30)))
names(arm0) = names(arm1) <- paste0('Category ', seq(1:4))
show(arm0)
show(arm1)
```

## Difference in Quantiles

To find a confidence interval and p-vaue for the difference in medians $q = 0.5$:
```{r}
# Confidence interval calculation.
ci <- QuantDiffCI(
  counts0 = arm0,
  counts1 = arm1,
  q = 0.5
)
round(ci, digits = 2)

# P-value calculation. 
pval <- QuantDiffP(
  counts0 = arm0,
  counts1 = arm1,
  q = 0.5
)
round(pval, digits = 2)
```

Note that the medians are linearly interpolated within integer bins. 

## Difference in Probability Indices

The difference in probability indices is defined as:
$$
\Delta = P(Y_{1} > Y_{0}) - P(Y_{0} > Y_{1}).
$$

To find a confidence interval and p-vaue for the difference in probability indices:
```{r}
# Confidence interval calculation.
ci <- ProbIndexDiffCI(
  counts0 = arm0,
  counts1 = arm1
)
round(ci, digits = 2)

# P-value calculation. 
pval <- ProbIndexDiffP(
  counts0 = arm0,
  counts1 = arm1
)
round(pval, digits = 2)
```